---
title: "FigureYa24 ROC"
author: "yeoli; Ying Ge, Yijing Chen"
date: "2025-5-20"
output: html_document
---

# Academic Citation
If you use this code in your work or research, we kindly request that you cite our publication:

Xiaofan Lu, et al. (2025). FigureYa: A Standardized Visualization Framework for Enhancing Biomedical Data Interpretation and Research Efficiency. iMetaMed. https://doi.org/10.1002/imm3.70005


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 需求描述
## Requirement description

用R画出ROC曲线（receiver operating characteristic curve）。

Draw the ROC curve in R（receiver operating characteristic curve）

## 应用场景
## Application scenario

在分类任务中，直观展示敏感性和特异性连续变量的综合指标。

场景一：比较多个biomarker或临床参数的诊断表现

场景二：比较多个算法的分类效果

Visualize composite metrics of sensitivity and specificity continuous variables in a classification task.

Scenario 1: Compare the diagnostic performance of multiple biomarkers or clinical parameters

Scenario 2: Compare the classification performance of multiple algorithms

## 输入文件
## Input data

包含至少两列，第一列是分组，此处第二列至第五列是miRNA的表达量。

It contains at least two columns, the first column is the group, and here the second to fifth columns are the miRNA expression.

```{r}
source("install_dependencies.R")
df <- read.table("easy_input.txt",head=T,sep="\t",check.names = F)
head(df)
```

## 开始画图
## Start drawing
