---
title: "FigureYa242corMethExpr"
author: "Xiaofan Lu"
reviewer: "Ying Ge, Junyi Shen"
date: "2025-5-20"
output: html_document
---

# Academic Citation
If you use this code in your work or research, we kindly request that you cite our publication:

Xiaofan Lu, et al. (2025). FigureYa: A Standardized Visualization Framework for Enhancing Biomedical Data Interpretation and Research Efficiency. iMetaMed. https://doi.org/10.1002/imm3.70005


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 需求描述 / Requirements Description
# FPKM跟启动子区甲基化的相关性。输入数据是TCGA的FPKM和DNA甲基化数据。 / Correlation between FPKM and promoter methylation. Input data is TCGA FPKM and DNA methylation data.

# 希望能学习到怎么获取基因启动子区的甲基化探针，自己跑代码时就能灵活自定义将启动子区调整TSS1500，TSS200，甚至分析gene body区域甲基化与基因表达的关系。 / Hope to learn how to obtain methylation probes in gene promoter regions, and be able to flexibly customize promoter regions like TSS1500, TSS200, and even analyze the relationship between gene body methylation and gene expression.

# 出自 / From: https://academic.oup.com/nar/article/48/D1/D856/5584613

# 应用场景 / Application Scenario
# 计算特定基因启动子DNA甲基化与对应表达谱的相关性并绘图。 / Calculate and plot the correlation between specific gene promoter DNA methylation and corresponding expression profiles.

# 环境设置 / Environment Setup


```{r}
source("install_dependencies.R")

```

# 加载包 / Load packages

```{r}
library(TCGAbiolinks)
library(ChAMPdata)
library(data.table)
data(probe.features) # 加载450甲基化探针注释文件 / Load 450k methylation probe annotation file

Sys.setenv(LANGUAGE = "en") #显示英文报错信息 / Display error messages in English
options(stringsAsFactors = FALSE) #禁止chr转成factor / Prevent chr from converting to factor
```

# 输入文件

TCGA-UCEC.methylation450.tsv.gz，UCEC的DNA甲基化数据，下载自XENA<https://xenabrowser.net/datapages/?dataset=TCGA-UCEC.methylation450.tsv&host=https%3A%2F%2Fgdc.xenahubs.net&removeHub=https%3A%2F%2Fxena.treehouse.gi.ucsc.edu%3A443>。已上传至微云<https://share.weiyun.com/Qn0X57I0>
