---
title: "FigureYa9 heatmap"
author: "Ying Ge; Yijing Chen"
date: "2025-5-20"
output: html_document
---

# Academic Citation
If you use this code in your work or research, we kindly request that you cite our publication:

Xiaofan Lu, et al. (2025). FigureYa: A Standardized Visualization Framework for Enhancing Biomedical Data Interpretation and Research Efficiency. iMetaMed. https://doi.org/10.1002/imm3.70005


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 需求描述
## Requirement description

用R代码画出paper里的热图heatmap

Draw heatmap in paper with R code

## 使用场景
## Usage scenario

场景一：sample间的相关性，用来评价生物学重复之间的重复性，或者体现不同组的差异

场景二：基因的表达变化聚类、sample聚类

Scenario 1: Correlation between samples, used to assess the reproducibility among biological replicates or to reflect differences between various groups.

Scenario 2: Clustering of Gene Expression Changes, Clustering of Samples

## 输入数据
## Input data

```{r}
source("install_dependencies.R")
df<-read.table("mRNA.txt",row.names = 1,header = T,as.is = T)
df[1:3,1:3]
#查看一共有多少个基因，多少个sample
#check the number of genes and samples in total
dim(df)
```

## 开始画图
## Start drawing

### 场景一：sample间的相关性，用来评价生物学重复之间的重复性，或者不同组的差异
### Scenario 1: Correlation between samples, used to assess the reproducibility among biological replicates or to reflect differences between various groups
